---
title: "Project2-MLR"
output: html_document
date: '2022-08-10'
---

```{r}
Data <- read.csv('kc_house_data.csv')
head(Data)
```

```{r}
library(ggplot2)
set.seed(1)
sample<-sample.int(nrow(Data), floor(.5*nrow(Data))) # 50/50 split
train<-Data[sample, ] # training data frame
test<-Data[-sample, ] # test data frame
```


```{r}
result<-lm(price~bedrooms+bathrooms+sqft_living+sqft_lot+floors+waterfront+view+condition+grade+sqft_above+sqft_basement+yr_built+yr_renovated+lat+long, data=train)
summary(result)
```
Insignificant coefficients: sqft_lot, floors, and yr_renovated

Conduct partial f-test:
Null hypothesis: H0: sqft_lot = floors = yr_renovated = 0 -> null hypothesis supports going with the reduced model by dropping sqft_lot, floors, and yr_renovated
Alternative hypothesis: Ha:at least one of the coefficients in H0 is not 0 ->  alternative hypothesis supports the full model by not sqft_lot, floors, and yr_renovated

```{r}
reduced<-lm(price~bedrooms+bathrooms+sqft_living+waterfront+view+condition+grade+sqft_above+sqft_basement+yr_built+lat+long, data=train)

anova(reduced,result)
```
F-Statistic: 1.2238; P-Value: 0.2993
Fail to reject null hypothesis, little evidence of supporting full model; go with reduced model

The Partial F-Test did not rule out any aesthetic predictors, but it removed three structural predictors.  

```{r}
library(faraway)
vif(result)
```
yr_renovated has multicollinearity, so we can drop it.

```{r}
ggplot(Data, aes(x=grade, y=view, color=lat))+
geom_point()+
geom_smooth(method=lm, se=FALSE)+
labs(title="Scatterplot of Wine Quality against Flavor, by Region")
```


